---
title: "The next blockbuster hit"
author: "stefania, will, joao, miguel"
output:
  html_document:
    css: AnalyticsStyles/default.css
    theme: paper
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: yes
  pdf_document:
    includes:
      in_header: AnalyticsStyles/default.sty
always_allow_html: yes
---

<hr>\clearpage

# The Business Questions

TEXT

# The Process

The "high level" process template is split in 3 parts, corresponding to the course sessions 3-4, 5-6, and an optional last part: 

1. *Part 1*: We use some of the survey questions (e.g. in this case the first 29 "attitude" questions) to find **key customer descriptors** ("factors") using *dimensionality reduction* techniques described in the [Dimensionality Reduction](http://inseaddataanalytics.github.io/INSEADAnalytics/CourseSessions/Sessions23/FactorAnalysisReading.html) reading of Sessions 3-4.

2. *Part 2*: We use the selected customer descriptors to **segment the market** using *cluster analysis* techniques described in the [Cluster Analysis ](http://inseaddataanalytics.github.io/INSEADAnalytics/CourseSessions/Sessions45/ClusterAnalysisReading.html) reading of Sessions 5-6.

3. *Part 3*: For the market segments we create, we will use *classification analysis* to classify people based on whether or not they have purchased a product and find what are the **key purchase drivers per segment**. For this part we will use [classification analysis ](http://inseaddataanalytics.github.io/INSEADAnalytics/CourseSessions/Sessions67/ClassificationAnalysisReading.html) techniques.

TEXT

```{r setuplibraries, echo=FALSE, message=FALSE}
suppressWarnings(source("AnalyticsLibraries/library.R"))
# Package options
suppressWarnings(ggthemr('fresh'))  # ggplot theme
opts_knit$set(progress=FALSE, verbose=FALSE)
opts_chunk$set(echo=FALSE, fig.align="center", fig.width=10, fig.height=6.35, results="asis")
options(knitr.kable.NA = '')
```

<hr>\clearpage

# The Data

First we load the data to use (see the raw .Rmd file to change the data file as needed):

```{r setupdata1E, echo=TRUE, tidy=TRUE}
# Please ENTER the name of the file with the data used. The file should be a .csv with one row per observation (e.g. person) and one column per attribute. Do not add .csv at the end, make sure the data are numeric.
datafile_name = "Dataset/IMDB-database.csv"

# Please enter the maximum number of observations to show in the report and slides. 
# DEFAULT is 10. If the number is large the report may be slow.
max_data_report = 10
```

# Making the data numeric

```{r}
ProjectData <- read.csv(datafile_name)
startProjectData <- as.matrix(ProjectData)
ProjectData <- as.matrix(ProjectData)

topdirnames = tail(names(sort(table(ProjectData[,"director_name"]))), 20)
hastopdirector = ProjectData[,"director_name"] %in% topdirnames
datafile_topnames = "Dataset/top20actors&directors.csv"
Topnames <- read.csv(datafile_topnames)
Topnames <- as.matrix(Topnames)
Topnames<-Topnames[,1]

hastopactor1 = ProjectData[,"actor_1_name"] %in% Topnames
hastopactor2 = ProjectData[,"actor_2_name"] %in% Topnames
hastopactor3 = ProjectData[,"actor_3_name"] %in% Topnames
net_USD= as.numeric(ProjectData[,"net_USD"])
cast_facebook_likes= as.numeric(ProjectData[,"cast_total_facebook_likes"])
movieposter_faces= as.numeric(ProjectData[,"facenumber_in_poster"])
movie_year= as.numeric(ProjectData[,"title_year"])
actor1_fb_likes = as.numeric(ProjectData[,"actor_1_facebook_likes"])
actor2_fb_likes = as.numeric(ProjectData[,"actor_2_facebook_likes"])
actor3_fb_likes = as.numeric(ProjectData[,"actor_3_facebook_likes"])
movie_fb_likes= as.numeric(ProjectData[,"movie_facebook_likes."])
number_votes = as.numeric(ProjectData[,"num_voted_users"])
movie_duration = as.numeric(ProjectData[,"duration"])
movie_budget= as.numeric(ProjectData[,"budget_USD"])
movie_profitable = as.numeric(ProjectData[,"profitable"])
director_fb_likes= as.numeric(ProjectData[,"director_facebook_likes"])
number_reviews= as.numeric(ProjectData[,"num_user_for_reviews"])
numeric_projectdata = cbind(as.numeric(ProjectData[,"movie_ID"]),hastopactor1,hastopactor2,hastopactor3,hastopdirector,net_USD,cast_facebook_likes,movieposter_faces,movie_year,actor1_fb_likes,actor2_fb_likes,actor3_fb_likes,movie_fb_likes,number_votes,movie_duration,movie_budget,movie_profitable,director_fb_likes,number_reviews)

```
#scaling the data
```{r}

ProjectData_scaled = apply(numeric_projectdata,2 , function(r) {
    if (sd(r) != 0) 
        res = (r - mean(r))/sd(r) else res = 0 * r
    res
})
```
# Part 2: Some descriptive statistics

```{r setupfactor, echo=TRUE, tidy=TRUE}
# Please ENTER then original raw attributes to use. 
# Please use numbers, not column names, e.g. c(1:5, 7, 8) uses columns 1,2,3,4,5,7,8
factor_attributes_used = c(2:20)
# Please ENTER the selection criterions for the factors to use. 
# Choices: "eigenvalue", "variance", "manual"
factor_selectionciterion = "manual"

# Please ENTER the desired minumum variance explained 
# (Only used in case "variance" is the factor selection criterion used). 
minimum_variance_explained = 65  # between 1 and 100

# Please ENTER the number of factors to use 
# (Only used in case "manual" is the factor selection criterion used).
manual_numb_factors_used = 7

# Please ENTER the rotation eventually used (e.g. "none", "varimax", "quatimax", "promax", "oblimin", "simplimax", and "cluster" - see help(principal)). Default is "varimax"
rotation_used = "varimax"

```

```{r}
factor_attributes_used <- intersect(factor_attributes_used, 1:ncol(ProjectData_scaled))
ProjectDataFactor <- ProjectData_scaled[,factor_attributes_used]
ProjectDataFactor <- ProjectData <- data.matrix(ProjectDataFactor)
```
Start by some basic visual exploration of, say, a few data:

```{r}
rownames(ProjectDataFactor) <- paste0("Obs.", sprintf("%02i", 1:nrow(ProjectDataFactor)))
iprint.df(t(head(round(ProjectDataFactor, 2), max_data_report)))
```

The data we use here have the following descriptive statistics: 

```{r}
iprint.df(round(my_summary(ProjectDataFactor), 2))
```

## Step 3: Check Correlations

This is the correlation matrix of the customer responses to the `r ncol(ProjectDataFactor)` attitude questions - which are the only questions that we will use for the segmentation (see the case):

```{r}
thecor = round(cor(ProjectDataFactor),2)
iprint.df(round(thecor,2), scale=TRUE)
```


```{r}
# Here is how the `principal` function is used 
UnRotated_Results<-principal(ProjectDataFactor, nfactors=ncol(ProjectDataFactor), rotate="none",score=TRUE)
UnRotated_Factors<-round(UnRotated_Results$loadings,2)
UnRotated_Factors<-as.data.frame(unclass(UnRotated_Factors))
colnames(UnRotated_Factors)<-paste("Comp",1:ncol(UnRotated_Factors),sep="")
```

```{r}
# Here is how we use the `PCA` function 
Variance_Explained_Table_results<-PCA(ProjectDataFactor, graph=FALSE)
Variance_Explained_Table<-Variance_Explained_Table_results$eig
Variance_Explained_Table_copy<-Variance_Explained_Table

rownames(Variance_Explained_Table) <- paste("Component", 1:nrow(Variance_Explained_Table), sep=" ")
colnames(Variance_Explained_Table) <- c("Eigenvalue", "Pct of explained variance", "Cumulative pct of explained variance")
```

Let's look at the **variance explained** as well as the **eigenvalues** (see session readings):

```{r}
iprint.df(round(Variance_Explained_Table, 2))
```

```{r}
eigenvalues  <- Variance_Explained_Table[, "Eigenvalue"]
df           <- cbind(as.data.frame(eigenvalues), c(1:length(eigenvalues)), rep(1, length(eigenvalues)))
colnames(df) <- c("eigenvalues", "components", "abline")
iplot.df(melt(df, id="components"))
```



## Step 5: Interpret the factors

Let's now see how the "top factors" look like. 

```{r}
if (factor_selectionciterion == "eigenvalue")
  factors_selected = sum(Variance_Explained_Table_copy[,1] >= 1)
if (factor_selectionciterion == "variance")
  factors_selected = 1:head(which(Variance_Explained_Table_copy[,"cumulative percentage of variance"]>= minimum_variance_explained),1)
if (factor_selectionciterion == "manual")
  factors_selected = manual_numb_factors_used
```

To better visualize them, we will use what is called a "rotation". There are many rotations methods. In this case we selected the `r rotation_used` rotation. For our data, the `r factors_selected` selected factors look as follows after this rotation: 

```{r}
Rotated_Results<-principal(ProjectDataFactor, nfactors=max(factors_selected), rotate=rotation_used,score=TRUE)
Rotated_Factors<-round(Rotated_Results$loadings,2)
Rotated_Factors<-as.data.frame(unclass(Rotated_Factors))
colnames(Rotated_Factors)<-paste("Comp.",1:ncol(Rotated_Factors),sep="")

sorted_rows <- sort(Rotated_Factors[,1], decreasing = TRUE, index.return = TRUE)$ix
Rotated_Factors <- Rotated_Factors[sorted_rows,]

iprint.df(Rotated_Factors, scale=TRUE)
```

To better visualize and interpret the factors we often "suppress" loadings with small values, e.g. with absolute values smaller than 0.5. In this case our factors look as follows after suppressing the small numbers:

```{r}
Rotated_Factors_thres <- Rotated_Factors
MIN_VALUE<-0.5
Rotated_Factors_thres[abs(Rotated_Factors_thres) < MIN_VALUE]<-NA
colnames(Rotated_Factors_thres)<- colnames(Rotated_Factors)
rownames(Rotated_Factors_thres)<- rownames(Rotated_Factors)

iprint.df(Rotated_Factors_thres, scale=TRUE)
```


## Step 6:  Save factor scores 

We can now either replace all initial variables used in this part with the factors scores or just select one of the initial variables for each of the selected factors in order to represent that factor. Here is how the factor scores  are for the first few respondents:

```{r}
NEW_ProjectData <- round(Rotated_Results$scores[,1:factors_selected,drop=F],2)
colnames(NEW_ProjectData)<-paste("DV (Factor)",1:ncol(NEW_ProjectData),sep=" ")

iprint.df(t(head(NEW_ProjectData, 10)), scale=TRUE)
```




#Part 3 Classification
```{r}
Istop250 = as.numeric(startProjectData[,"imdb_top_250"])
ProjectClass<-cbind(Istop250,NEW_ProjectData)

# Please ENTER the class (dependent) variable:
# Please use numbers, not column names! e.g. 82 uses the 82nd column are dependent variable.
# YOU NEED TO MAKE SURE THAT THE DEPENDENT VARIABLES TAKES ONLY 2 VALUES: 0 and 1!!!
dependent_variable= 1

# Please ENTER the attributes to use as independent variables 
# Please use numbers, not column names! e.g. c(1:5, 7, 8) uses columns 1,2,3,4,5,7,8
independent_variables= c(2:8)

# Please ENTER the profit/cost values for the correctly and wrong classified data:
actual_1_predict_1 = 100
actual_1_predict_0 = 0
actual_0_predict_1 = -1
actual_0_predict_0 = 0
```
```{r}


# Please ENTER the probability threshold above which an observations  
# is predicted as class 1:
Probability_Threshold=70 # between 1 and 99%

# Please ENTER the percentage of data used for estimation
estimation_data_percent = 80
validation_data_percent = 10

# Please enter 0 if you want to "randomly" split the data in estimation and validation/test
random_sampling = 0

# Tree parameter
# PLEASE ENTER THE Tree (CART) complexity control cp (e.g. 0.001 to 0.02, depending on the data)
CART_cp = 0.02

# Please enter the minimum size of a segment for the analysis to be done only for that segment
min_segment = 100
```

```{r}
ProjectData = ProjectClass # Just to initialize the data

Probability_Threshold = Probability_Threshold/100 # make it between 0 and 1

dependent_variable = unique(sapply(dependent_variable,function(i) min(ncol(ProjectData), max(i,1))))
independent_variables = unique(sapply(independent_variables,function(i) min(ncol(ProjectData), max(i,1))))
```
#if (length(unique(ProjectData[,dependent_variable])) !=2){
  cat("\n*****\n BE CAREFUL, THE DEPENDENT VARIABLE TAKES MORE THAN 2 VALUES...")
  cat("\nSplitting it around its median...\n*****\n ")
  new_dependent = ProjectData[,dependent_variable] >= median(ProjectData[,dependent_variable])
  ProjectData[,dependent_variable] <- 1*new_dependent
}
```{r}
Profit_Matrix = matrix(c(actual_1_predict_1, actual_0_predict_1, actual_1_predict_0, actual_0_predict_0), ncol=2)
colnames(Profit_Matrix)<- c("Predict 1", "Predict 0")
rownames(Profit_Matrix) <- c("Actual 1", "Actual 0")
test_data_percent = 100-estimation_data_percent-validation_data_percent
CART_control = rpart.control(cp = CART_cp)
```



This is a "small tree" classification for example:

```{r}
# FIrst we split the data in estimation, validation, and test

if (random_sampling){
  estimation_data_ids=sample.int(nrow(ProjectData),floor(estimation_data_percent*nrow(ProjectData)/100))
  non_estimation_data = setdiff(1:nrow(ProjectData),estimation_data_ids)
  validation_data_ids=non_estimation_data[sample.int(length(non_estimation_data), floor(validation_data_percent/(validation_data_percent+test_data_percent)*length(non_estimation_data)))]
  } else {
    estimation_data_ids=1:floor(estimation_data_percent*nrow(ProjectData)/100)
    non_estimation_data = setdiff(1:nrow(ProjectData),estimation_data_ids)
    validation_data_ids = (tail(estimation_data_ids,1)+1):(tail(estimation_data_ids,1) + floor(validation_data_percent/(validation_data_percent+test_data_percent)*length(non_estimation_data)))
    }

test_data_ids = setdiff(1:nrow(ProjectData), union(estimation_data_ids,validation_data_ids))

estimation_data=ProjectData[estimation_data_ids,]
validation_data=ProjectData[validation_data_ids,]
test_data=ProjectData[test_data_ids,]
```

```{r}
# just name the variables numerically so that they look ok on the tree plots
independent_variables_nolabel = paste("IV", 1:length(independent_variables), sep="")

estimation_data_nolabel = cbind(estimation_data[,dependent_variable], estimation_data[,independent_variables])
colnames(estimation_data_nolabel)<- c(colnames(estimation_data)[dependent_variable],independent_variables_nolabel)

validation_data_nolabel = cbind(validation_data[,dependent_variable], validation_data[,independent_variables])
colnames(validation_data_nolabel)<- c(dependent_variable,independent_variables_nolabel)

test_data_nolabel = cbind(test_data[,dependent_variable], test_data[,independent_variables])
colnames(test_data_nolabel)<- c(dependent_variable,independent_variables_nolabel)

estimation_data_nolabel = data.frame(estimation_data_nolabel)
validation_data_nolabel = data.frame(validation_data_nolabel)
test_data_nolabel = data.frame(test_data_nolabel)

estimation_data = data.frame(estimation_data)
validation_data = data.frame(validation_data)
test_data = data.frame(test_data)
```

```{r}
formula=paste(colnames(estimation_data)[dependent_variable],paste(Reduce(paste,sapply(head(independent_variables_nolabel,-1), function(i) paste(i,"+",sep=""))),tail(independent_variables_nolabel,1),sep=""),sep="~")
CART_tree<-rpart(formula, data= estimation_data_nolabel,method="class", control=CART_control)

rpart.plot(CART_tree, box.palette="OrBu", type=3, extra=1, fallen.leaves=F, branch.lty=3)
```

```{r}
CART_tree_large<-rpart(formula, data= estimation_data_nolabel,method="class", control=rpart.control(cp = 0.001))
rpart.plot(CART_tree_large, box.palette="OrBu", type=3, extra=1, fallen.leaves=F, branch.lty=3)
```

```{r}
# Let's first calculate all probabilites for the estimation, validation, and test data
estimation_Probability_class1_tree<-predict(CART_tree, estimation_data_nolabel)[,2]
estimation_Probability_class1_tree_large<-predict(CART_tree_large, estimation_data_nolabel)[,2]

validation_Probability_class1_tree<-predict(CART_tree, validation_data_nolabel)[,2]
validation_Probability_class1_tree_large<-predict(CART_tree_large, validation_data_nolabel)[,2]

test_Probability_class1_tree<-predict(CART_tree, test_data_nolabel)[,2]
test_Probability_class1_tree_large<-predict(CART_tree_large, test_data_nolabel)[,2]


estimation_prediction_class_tree=1*as.vector(estimation_Probability_class1_tree > Probability_Threshold)
estimation_prediction_class_tree_large=1*as.vector(estimation_Probability_class1_tree_large > Probability_Threshold)

validation_prediction_class_tree=1*as.vector(validation_Probability_class1_tree > Probability_Threshold)
validation_prediction_class_tree_large=1*as.vector(validation_Probability_class1_tree_large > Probability_Threshold)

test_prediction_class_tree=1*as.vector(test_Probability_class1_tree > Probability_Threshold)
test_prediction_class_tree_large=1*as.vector(test_Probability_class1_tree_large > Probability_Threshold)
```

```{r}
formula_log=paste(colnames(estimation_data[,dependent_variable,drop=F]),paste(Reduce(paste,sapply(head(independent_variables,-1), function(i) paste(colnames(estimation_data)[i],"+",sep=""))),colnames(estimation_data)[tail(independent_variables,1)],sep=""),sep="~")

logreg_solution <- glm(formula_log, family=binomial(link="logit"),  data=estimation_data)

log_coefficients = round(summary(logreg_solution)$coefficients,1)
iprint.df(log_coefficients)

```

```{r}
estimation_Probability_class1_log<-predict(logreg_solution, type="response", newdata=estimation_data[,independent_variables])
validation_Probability_class1_log<-predict(logreg_solution, type="response", newdata=validation_data[,independent_variables])
test_Probability_class1_log<-predict(logreg_solution, type="response", newdata=test_data[,independent_variables])

estimation_prediction_class_log=1*as.vector(estimation_Probability_class1_log > Probability_Threshold)
validation_prediction_class_log=1*as.vector(validation_Probability_class1_log > Probability_Threshold)
test_prediction_class_log=1*as.vector(test_Probability_class1_log > Probability_Threshold)
```

After also running the large tree and the logistic regression classifiers, we can then check how much "weight" these three methods put on the different purchase drivers (Q16 of the survey):

```{r}
log_importance = tail(log_coefficients[,"z value", drop=F],-1) # remove the intercept
log_importance = log_importance/max(abs(log_importance))

tree_importance = CART_tree$variable.importance
tree_ordered_drivers = as.numeric(gsub("\\IV"," ",names(CART_tree$variable.importance)))
tree_importance_final = rep(0,length(independent_variables))
tree_importance_final[tree_ordered_drivers] <- tree_importance
tree_importance_final <- tree_importance_final/max(abs(tree_importance_final))
tree_importance_final <- tree_importance_final*sign(log_importance)

large_tree_importance = CART_tree_large$variable.importance
large_tree_ordered_drivers = as.numeric(gsub("\\IV"," ",names(CART_tree_large$variable.importance)))
large_tree_importance_final = rep(0,length(independent_variables))
large_tree_importance_final[large_tree_ordered_drivers] <- large_tree_importance
large_tree_importance_final <- large_tree_importance_final/max(abs(large_tree_importance_final))
large_tree_importance_final <- large_tree_importance_final*sign(log_importance)

Importance_table <- cbind(tree_importance_final,large_tree_importance_final, log_importance)
colnames(Importance_table) <- c("CART 1", "CART 2", "Logistic Regr.")
rownames(Importance_table) <- rownames(log_importance)

iprint.df(Importance_table)
```

Finally, if we were to use the estimated classification models on the test data, we would get the following profit curves (see the raw .Rmd file to select the business profit parameters). 

The profit curve using the small classification tree: 

```{r}
actual_class<- test_data[,dependent_variable]

probs = test_Probability_class1_tree
xaxis = sort(unique(c(0,1,probs)), decreasing = TRUE)
res = Reduce(cbind,lapply(xaxis, function(prob){
  useonly = which(probs >= prob)
  predict_class = 1*(probs >= prob)
  theprofit = Profit_Matrix[1,1]*sum(predict_class==1 & actual_class ==1)+
    Profit_Matrix[1,2]*sum(predict_class==0 & actual_class ==1)+
    Profit_Matrix[2,1]*sum(predict_class==1 & actual_class ==0)+
    Profit_Matrix[2,2]*sum(predict_class==0 & actual_class ==0)
  
  c(100*length(useonly)/length(actual_class), theprofit) 
  }))
xaxis = res[1,]; yaxis = res[2,]
df<-data.frame(Percentile = xaxis, Profit = yaxis)
iplot.df(df, x="Percentile", y="Profit", v=NULL)

best_profits_small_tree = df[which.max(df$Profit),]
```

The profit curve using the large classification tree: 

```{r}
probs = test_Probability_class1_tree_large
xaxis = sort(unique(c(0,1,probs)), decreasing = TRUE)
res = Reduce(cbind,lapply(xaxis, function(prob){
  useonly = which(probs >= prob)
  predict_class = 1*(probs >= prob)
  theprofit = Profit_Matrix[1,1]*sum(predict_class==1 & actual_class ==1)+
    Profit_Matrix[1,2]*sum(predict_class==0 & actual_class ==1)+
    Profit_Matrix[2,1]*sum(predict_class==1 & actual_class ==0)+
    Profit_Matrix[2,2]*sum(predict_class==0 & actual_class ==0)
  
  c(100*length(useonly)/length(actual_class), theprofit) 
  }))
xaxis = res[1,]; yaxis = res[2,]
names(xaxis)<- NULL; names(yaxis) <- NULL
df<-data.frame(Percentile = xaxis, Profit = yaxis)
iplot.df(df, x="Percentile", y="Profit", v=NULL)

best_profits_large_tree = df[which.max(df$Profit),]
```

The profit curve using the logistic regression classifier: 

```{r}
probs = test_Probability_class1_log
xaxis = sort(unique(c(0,1,probs)), decreasing = TRUE)
res = Reduce(cbind,lapply(xaxis, function(prob){
  useonly = which(probs >= prob)
  predict_class = 1*(probs >= prob)
  theprofit = Profit_Matrix[1,1]*sum(predict_class==1 & actual_class ==1)+
    Profit_Matrix[1,2]*sum(predict_class==0 & actual_class ==1)+
    Profit_Matrix[2,1]*sum(predict_class==1 & actual_class ==0)+
    Profit_Matrix[2,2]*sum(predict_class==0 & actual_class ==0)
  
  c(100*length(useonly)/length(actual_class), theprofit) 
  }))
xaxis = res[1,]; yaxis = res[2,]
names(xaxis)<- NULL; names(yaxis) <- NULL
df<-data.frame(Percentile = xaxis, Profit = yaxis)
iplot.df(df, x="Percentile", y="Profit", v=NULL)

best_profits_logistic = df[which.max(df$Profit),]
```

These are the maximum total profit achieved in the test data using the three classifiers (without any segment specific analysis so far).

```{r}
best_profits = rbind(best_profits_small_tree, best_profits_large_tree, best_profits_logistic)
rownames(best_profits) <- c("Small Tree", "Large Tree", "Logistic Regression")
iprint.df(round(best_profits, 2))
```
